Preparing a manuscript for a peer-reviewed journal the FMDL way

### 2021-07-27 IITD_Manuscript.tex
Updated

First some ground rules for labeling: sec for sections, fig for figures, tbl for tables.

@@

@@

FA and TA (PhD fellowships) and PS (postdoc fellowship) acknowledge support from Ministry of Human Resource \& Development (MHRD). SA acknowledges support from University Grants Commission. CP acknowledges partial support from grant XYZ from Department of Science \& Technology. PS and CA acknowledges support from grant ABC from Department of Science \& Technology. All authors acknowledge facility access to Central Research Facility (CRF) and Nanoscale Research Facility (NRF, NNetra program) at IIT Delhi. Authors acknowledge technical assistance from Mr. Did Occasional Measurements/Process Runs of CRF.

>>>>

@@

The label in Fig.~(\ref{fig:cv}) is an example of a cross-reference. You \textbf{never} use absolute references in a document (like \verb|Fig.~1|). The reason for this ought to be obvious - while you author a text, things can move around, and you do not want to keep track of what moves where. \LaTeX\ is supposed to take care of that - not you. You can make mistakes, and mistakes can be costly.

An equation can be similarly labelled:

\begin{align}
  E^{2} = p^{2} c^{2} + m_{0}^{2} c^{4} \label{eqn:relativistic4vector}
\end{align}

Not all equations need labels like Eq.~(\ref{eqn:relativistic4vector}) of course:

\begin{align}
  E & = h\nu \nonumber \\
  & \equiv \frac{h c}{\lambda} \label{eqn:plancksrelationship}
\end{align}

In labeling (and referencing equations), be conservative. Label only those specific (and few) equations that you are actually going to use. Remember - any text can be made to look more inaccessible by involving more math. You should not show all steps in a paper, just the important ones that help you make your point. Needless to add, all your analytical calculations should be cross-checked with Maxima or Mathematica before it gets on your manuscript.

Tables can be similarly cross-referenced as shown in Table~\ref{tbl:ratio}.

\begin{table}
  \caption{An example table}
  \label{tbl:ratio}
  \begin{center}
    \begin{tabular}{cccccc}
      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
      \hline \\
         & (nm) & & K/A & Na/A & Nb/A \\
      \hline \\
      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
         & & & (0.3375) & (0.6624) & (1.028) \\
      \hline \\
      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
         & & & (0.5091) & (0.4910) & (1.037) \\
      \hline \\
      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
         & & & (0.7682) & (0.2317) & (1.153) \\
      \hline \\
    \end{tabular}
  \end{center}
\end{table}

Needless to add, you need to pick labels that reflect the contents of the object being referenced.

Notice some ground rules for labeling: sec for sections, fig for figures, tbl for tables. This convention, that I follow in my documents, helps distinguish between the objects that are being referenced. It is for your own benefit of course.

@@

FA and TA (PhD fellowships) and PS (postdoc fellowship) acknowledge support from Ministry of Human Resource \& Development (MHRD). SA acknowledges support from University Grants Commission. CP acknowledges partial support from grant XYZ from Department of Science \& Technology. PS and MS acknowledges support from grant ABC from Department of Science \& Technology. All authors acknowledge facility access to Central Research Facility (CRF) and Nanoscale Research Facility (NRF, NNetra program) at IIT Delhi. Authors acknowledge technical assistance from Mr. Did Occasional Measurements/Process Runs of CRF.
